Experiences in teaching with Jupyter, Jupyterhub, and nbgrader

### 2019-09-24 paper/paper.tex

>>>>

Using technology in everyday teaching is something that we, as instructors, 
should all consider. Using technology for educational purposes is the key to moderate 
the gap between students of the new era, students who are being brought up and with 
technology, and us the instructors of the old era, who were brought up with no internet 
available and are trying to catch up with technology.
